Different rules for binocular combination of luminance flicker in cortical and subcortical pathways

### 2023-06-22 manuscript.Rmd
Added option to delete raw data files after use - necessary because Github Actions otherwise doesn't have enough space

processdata <- 3  # this flag determines the amount of processing, with 4 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data
# 2 - average data across participants, do bootstrapping
# 3 - download all raw data and analyse (requires 48GB of storage)

@@

@@

    save(file=paste0(datadir,'P',150+participant,'summary.RData'),list=c('cleanmeansE','meanspec'))
    }

@@

>>>>

processdata <- 3  # this flag determines the amount of processing, with 4 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data
# 2 - average data across participants, do bootstrapping
# 3 - download all raw data and analyse (requires 48GB of storage)
cleanupraw <- 1  # if downloading raw data, delete once processed to save space

@@

 if (cleanupraw==1){file.remove(d)} # delete raw data files to save space
      }

@@

    save(file=paste0(datadir,'P',150+participant,'summary.RData'),list=c('cleanmeansE','meanspec'))
    if (cleanupraw==1){file.remove(d)}  # delete raw data files to save space
    }

@@

 if (cleanupraw==1){file.remove(d)} # delete raw data files to save space
